\meta{Version 2011-12-07 by Elad Schiller.}

All of the courses in the MPCSN programme have being running for
several years and they all provide the student with important
engineering skills. Each course in the programme includes several home
assignments, labs, programming projects and exercises. In addition,
key professional skills are examined in the final written exams that
each course has.

A partial list the professional skills that the CSN programme provides
are listed below.

\paragraph{CSN1} Demonstrate knowledge in computer systems and
networks with emphasis on algorithm design, and computer programming
and with proven experience as well as insights of current research and
development.

Courses: FaultTol, CompNet, AdvCSN, DistSys, RealTime.

\paragraph{CSN2} Demonstrate the ability to develop and design
computer algorithms, programs, network protocols, services and
innovation in these areas, which are adapted to the needs and
capacities of their users, and which meet the societal requirements of
sustainable development in economical, social and ecological terms.

Courses: CompNet, AdvDistSys, ParDistRTS, CompSec, NetSec, AdvCSN,
MScAoA.

\paragraph{CSN3} Demonstrate both a wide knowledge in the specific
technical subject, including mathematics and related sciences, as well
as significant depth of knowledge in designing algorithms and
programming building computer systems and networks.

Courses: AdvDistSys, ParDistRTS, NetSec, Route, AdvCSN, MScAoA.

\paragraph{CSN4} Demonstrate the ability to work in teams and to
collaborate in groups with different constitutions and backgrounds in
algorithms, programming and cyber-physical systems.

Courses: ParDistRTS, MScAoA, MScThesis.

\paragraph{CSN5} Demonstrate the ability to discuss and give a clear
account of his/her conclusions and the knowledge and arguments that
support these both orally and in writing addressing different
audiences in both national and international contexts.

Courses: FaultTol, AdvCSN, MScAoA, MScThesis.

\paragraph{CSN6} Demonstrate the ability to create, analyse and
critically evaluate different algorithmic designs and their
implementations in computer systems and networks.

Courses: FaultTol, CompNet, AdvDistSys, ParDistRTS, CompSec, NetSec,
AdvCSN, MScAoA, MScThesis.

\paragraph{CSN7} Demonstrate the ability to make assessments of
computer programs, and network protocols while taking into account
relevant analytical, societal and ethical aspects and show awareness
of ethical aspects on research and development, and to demonstrate
insights of the potential and limitations of computer and networks
technologies.

Courses: CompSec, AdvCSN.

\paragraph{CSN8} Demonstrate the ability, when given system settings,
to design efficient algorithms and program them in a variety of such
systems settings.

Courses: CompNet, AdvDistSys, RealTime, ParDistRTS, AdvCSN.

\paragraph{CSN9} Demonstrate insights of the potential and limitations
of computer and networks technologies, their role in society and the
designer responsibility for their use, with regards to social,
economical and environmental aspects including the working
environment.

Courses: FaultTol, CompNet, DistSys, AdvDistSys, CompSec, NetSec,
Route.

\paragraph{CSN10} Demonstrate the ability to identify his/her needs
for further knowledge and to continuously develop his/her competence,

Courses: FaultTol, CompNet, AdvDistSys, ParDistRTS, CompSec, NetSec,
AdvCSN, MScAoA, MScThesis.

\paragraph{CSN11} Plan and with adequate methods carry out qualified
tasks within given constraints or within a given framework. Within the
framework of computer systems, the considered methods are from the
areas of algorithm design and computer programming. Resources
efficiency is the main design and implementation constraint along with
usability of computer systems.

Courses: FaultTol, CompNet, DistSys, AdvDistSys, RealTime,
ParDistRTS, CompSec, NetSec, Route, AdvCSN, MScAoA, MScThesis.

\paragraph{Course abbreviations:}
\begin{description}
\item[AdvCSN    ] Advanced topics in computer systems and networks  (DAT145)
\item[AdvDistSys] Advanced Distributed systems                      (TDA297) 
\item[CompNet   ] Computer networks                                 (EDA387) 
\item[CompSec   ] Computer security                                 (EDA263) 
\item[DistSys   ] Distributed systems                               (TDA596) 
\item[FaultTol  ] Fault tolerant computer systems                   (DAT270) 
\item[MScAoA    ] Masterclass: Area of Advance                      (DATnnn) 
\item[NetSec    ] Network security                                  (EDA491) 
\item[ParDistRTS] Parallel and distributed real-time systems        (EDA421) 
\item[RealTime  ] Real time systems                                 (EDA222) 
\item[Route     ] Routing technology                                (LEU420) 
\end{description}

% \begin{tabular}{lcp{.6\columnwidth}}
%    AdvCSN     &=& DAT145 Advanced topics in computer systems and networks,
% \\ AdvDistSys &=& TDA297 Advanced Distributed systems,
% \\ CompNet    &=& EDA387 Computer networks,
% \\ CompSec    &=& EDA263 Computer security,
% \\ FaultTol   &=& DAT270 Dependable computer systems,
% \\ DistSys    &=& TDA596 Distributed systems,
% \\ MScAoA     &=& DATnnn Masterclass: Area of Advance,
% \\ NetSec     &=& EDA491 Network security,
% \\ ParDistRTS &=& EDA421 Parallel and distributed real-time systems,
% \\ RealTime   &=& EDA222 Real time systems,
% \\ Route      &=& LEU420 Routing technology.
% \end{tabular}
