\documentclass[11pt]{article} 
\renewcommand{\baselinestretch}{0.96}
\begin{document}
\title{\bf Computer Science -- Algorithms, Languages and Logic\\
M.Sc., 120 cr, 2 years}
\author{}
\date{}
\maketitle

\section*{Programme aim}

Computer systems are becoming increasingly powerful and intelligent, and they rely on increasingly sophisticated techniques. To master the complexity of these systems it is essential to understand the core areas of computer science. While computer systems and their applications develop rapidly, the
underlying foundations of computing are mature mathematical theories.

This programme offers a comprehensive foundation in the science of 
programming and computing, thus providing lasting knowledge in the field. It 
gives the student a strong basis for developing the computer applications of today and tomorrow and for conducting innovative research and promoting development.

After completion of their studies, the students shall be able to

\begin{itemize}
\item apply solid knowledge in the mathematical and logical foundations of computing, including aspects like tractability, complexity, correctness, and 
safety, 
\item create models that are both meaningful and amenable to analysis, thereby 
chosing the right level of abstraction,
\item develop correct and efficient computer programmes and systems that 
satisfy given requirements under given constraints,
\item analyze and test systems, evaluate, predict, prove and verify their 
essential properties, 
\item identify and handle complex computational problems, also within project 
work,
\item communicate their ideas and results to both specialists and nonspecialists, give structured and scholarly presentations in oral and
written form,
\item find scientific information and integrate knowledge, identify their own 
needs for gathering further knowledge and do the necessary self-study,
\item work in international environments,
\item critically judge systems, results, and the use of information technology 
also from a social point of view, and be aware that results of computations 
crucially depend on model assumptions.
\end{itemize}

\section*{Who should apply}

The programme is intended for students who wish to study the core areas of computer science on an advanced level in order to prepare themselves for research and development particularly in the software industry. It also 
provides an ideal basis for academic research in computer science.
 
Most students will have a BSc in computer science. However, the programme can also serve as a conversion course for students with BSc in related subjects, such as mathematics, physics or engineering sciences, provided they have basic knowledge of mathematics and programming, and have completed an introductory computer science course such as data structures or algorithms.

\section*{Why apply}

Students will obtain a strong computer science background and thus gain access 
to a wide range of opportunities in the information technology industry. 
Students acquire generic skills and lasting subject knowledge and are in a 
good position to understand and contribute to technological advances. Products 
and whole companies are based on advanced algorithmic techniques, and these 
industries employ skilled computer scientists. The programme also provides the 
students with an excellent background for future PhD studies in computing, 
which can lead to a career as an academic researcher or computing teacher.

\section*{Research connections}

Chalmers pursues vigorous and internationally recognized research, also in
cooperation with industry, in all core areas of the programme. Chalmers is 
well-known for its research in functional programming and played a major role 
in the design and development of the standard lazy functional language Haskell. Powerful software tools for testing and combinatorial problem solving 
have widespread use. Methods from programming language theory are applied to 
problems in security. Pioneering work is conducted in type theory and computer 
assisted theorem proving. Researchers in programming logic also collaborate 
with linguists in the field of natural language processing. Another important 
area is the design and analysis of algorithms and their applications in 
bioinformatics and networks in a broad sense, and in large-scale optimization. 
Teachers are active researchers in these fields, which gives the programme 
scientific quality and depth.

\section*{Specific eligibility}
\subsection*{Undergraduate profile}

Major in Computer Science, Computer Engineering, Mathematics, Engineering Physics or Information Engineering.
 
\subsection*{Prerequisites}

Mathematics (including Discrete Mathematics and Linear Algebra), Statistics, Programming, Algorithms and Data Structures.

\section*{Programme content}
 
The core of the programme covers four main branches of computer science:

\begin{itemize}
\item {\em Algorithms}, including artificial intelligence, machine learning 
and optimization,
\item {\em Logic}, including applications in hardware and software 
verification,
\item {\em Programming languages}, with underlying principles, implementation 
techniques and advanced programming techniques,
\item {\em Computer security}, including cryptography and language-based 
security. 
\end{itemize}

Students have to take the following core courses:

\begin{itemize}
\item Algorithms
\item Logic in Computer Science
\item Programming Language Technology
\end{itemize}

The optional segment of the programme offers the student a broad range of courses in other areas of computer science, bioinformatics, software engineering, mathematics, and other related fields.
 
At least 5 of the following profile courses, divided in 4 tracks, must be 
taken:

\begin{itemize}
\item {\bf Algorithms:} Advanced Algorithms, Discrete Optimization, Algorithms
for Machine Learning and Inference, Artificial Intelligence
\item {\bf Logic and Verification:} Models of Computation, 
Types for Programs and Proofs, Software Engineering using Formal Methods, 
Hardware Description and Verification\footnote{Under discussion, may be 
cancelled.}
\item {\bf Programming Languages:} Compiler Construction, Advanced Functional 
Programming, Frontiers of Programming Language Technology, Parallel
Functional Programming
\item {\bf Security:} (no core course) Cryptography, Programming Language 
Based Security
\end{itemize}

Students may specialize on a track or aim at a broader education and mix 
courses from several tracks. The curriculum is filled with 4 elective courses
that can be freely chosen and may also come from neighbored programmes. It is 
also possible to take an elective project course and PhD level courses.
However, all elective courses must have a clear relationship to the programme.

The programme is completed with a 30 points master's thesis.

\newpage
\section*{Appendix}

The programme has the ambition to offer the students a variety of courses that
are tied to the research strengths at the Department of Computer Science and
Engineering. It provides freedom of choice, thus enabling individual study 
plans, but at the same the tracks give guidance for meaningful paths to go.
The roles of most of the courses are detailed below.

\bigskip
The {\bf compulsory core courses} represent the three cornerstones of the 
programme: Algorithms, Logic in Computer Science, Programming Language 
Technology.

\bigskip
Courses in the {\bf Algorithms track} rely on the basic Algorithms course (or
knowledge gained in equivalent courses) and can be studied in any order.

{\bf Advanced Algorithms} is a generic algorithms course that covers the main
techniques of design and analysis of algorithms, but in selected fields it 
goes more into depth than the basic course. In particular it provides 
solution methods for computationally hard problems. It adopts a rigorous 
analytical approach and emphasizes correctness, efficiency, and accuracy.

{\bf Discrete Optimization}, in contrast, focuses on a special but very 
important class of problems, integer linear programs (ILP), and provides 
methods for modelling (that is, completely specifying) real-world optimization 
problems as ILP, as well as methods for solving them.

{\bf Algorithms for Machine Learning and Inference} is another specialized course. It shows how algorithms can extract information and automatically draw 
conclusions from data sets, on solid scientific grounds. 

{\bf Artificial Intelligence} (AI) has similar contents but a unique shape, 
consisting of a block of introductory lectures followed by projects to be 
carried out by small groups of students. Logic appears as a formalism to 
specify and solve problems in AI.

{\bf Structural Bioinformatics} is not among the profile courses but can be taken as a deepening course in Algorithms: Students with an interest in 
computational molecular biology learn about problems in this application 
domain that are accessible to the algorithmic methods seen in the other courses.

\bigskip
The {\bf Logic and Verification} track builds upon the compulsory Logic in 
Computer Science course. There is also some interaction with Programming 
Language Technology, thus students will be helped by having done this 
compulsory course before. However the profile courses can be read in any order. 

{\bf Models of Computation} is a course about formalisms that make the 
intuitive notion of computability explicit. 

{\bf Types for Programs and Proofs} gives broad knowledge of type systems for 
programming languages, including interactive programming and proof systems 
using dependent types. 

{\bf Software Engineering using Formal Methods} shows how to formally express 
and verify safety properties of programmes. This way it applies logic to
verification tools.

\bigskip
The {\bf Programming Languages} track comprises courses on several aspects of
programming languages, which is the main tool to make computers actually work. 

{\bf Compiler Construction} addresses the syntactic structure of programming 
languages, including type systems, and translation of source code into
executable code. It can be noticed that problems in run-time organization, 
code optimization, and register allocation build a bridge to the field of
discrete optimization.

{\bf Advanced Functional Programming} explores the powerful mechanisms that 
functional programming offers to solve real problems and to structure large programs. A focus is on library design, embedded languages, and types.
Specification, program properties, and reasoning about correctness are common 
themes in this master's programme.

{\bf Parallel Functional Programming} has been introduced as a course that 
contributes to the increasingly important area of parallelism (e.g., multi-core 
processors).

\bigskip
The {\bf Security} track is not directly built upon a core course but has obvious relationships to algorithms and problem complexity as well as programming languages and verification of properties: 

{\bf Cryptography} presents, among other topics, public key primitives based 
on the computational hardness of mathematical problems, hash functions as 
parts of cryptographic protocols, and security guarantees.

{\bf Programming Language Based Security} is based on the idea that many 
attacks work on the application level, and these are typically specified in 
programming languages. A direct benefit of language-based security is the 
ability to naturally express security policies using the well-developed area 
of programming languages.

\bigskip
The {\bf Project in Computer Science} is not a course in the usual sense, nor 
does it belong to a track. It gives students the opportunity to do supervised 
work on a freely chosen subject which, however, must fit in the programme and 
be nontrivial.

\end{document}
